---
title: "Workout 1"
author: "Antara Jha"
output: github_document
---
#Introduction
ANALYSIS OF GSW PLAYERS
This is an analysis of the performance of the starting 5 GSW players.

##Motivation
The Golden State Warriors capture the hearts of all sports fans in California, and being at UC Berkeley, we are not exempt. Thus, I have taken the initiative to analyze the performance of GSW and specifically of its 5 starting players.

##Background
The Golden State Warriors are an American professional basketball team based in Oakland, California. The Warriors compete in the National Basketball Association, as a member of the league's Western Conference Pacific Division. They are one of the most celebrated basketball teams ever!

For the Warriors, wild numbers are more than just wild. Some carry historical significance. Others lengthen their lead on a basketball world trying—and almost always failing—to keep up. 

##Data
The data that I have used combines a statistics about a variety of variables, right from their team details to the details of every shot they have taken (when was it taken? what kind of shot was it? did it go in?).

Here's an example of data on Stephen Curry:
```{r}
curry
```

##Analysis
The analysis involved cleaning the data, adding columns to better categorize the date (by player name), generating charts that make the observations and analysis more clear, and combining tables.

```{r out.width='80%', echo=FALSE, fig.align='center'}
knitr::include_graphics("/Users/antarajha/Desktop/hw-stat133/images/gsw_shots_chart")

```


